---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading neccessary libraries
```{r Initialize, warning=FALSE}
library(ggplot2)
```

## Loading and preprocessing the data

- **First read the raw data**
- **Then using "date" and "interval" to construct two new columns `time` and `hour`**

```{r cache=TRUE}
stepData = read.csv(unz("activity.zip", "activity.csv"), header=T, na="NA",
                   colClasses=c("integer", "character", "integer"))
stepData$time = strptime(paste(stepData$date, paste(stepData$interval %/% 100, 
                        stepData$interval %% 100, sep=":")), "%Y-%m-%d %H:%M")
stepData$hour = stepData$time$hour

```

## What is mean total number of steps taken per day?
The mean steps taken per day is `r round(sum(stepData$steps, na.rm=T)/length(unique(stepData$date)), 1)`


## What is the average daily activity pattern?

```{r}
hours = 0:23
avgStep = tapply(stepData$steps, stepData$hour, function(x) mean(x, na.rm=T))
#g = ggplot(data=stepData, aes(x=hour, y=steps))
g = ggplot(data=NULL, aes(x=hours, y=avgStep))
g + geom_histogram(stat="identity")
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?

```{r}
stepData$wday = factor(stepData$time$wday)
sapply(stepData$wday)
```